---
title: "Day 3 Activities"
author: "Heather"
format: html
editor: visual
execute: 
  warning: false
  echo: true
---

# Day 3 Activities

### Conditional Statements

```{r}
temperature <- 95

if (temperature > 97) {
  print("Temperature Warning")
} else {
  print("No temperature Warning")
}
```

Create an if else statement for blue whale lengths. create a variable bluewhale which has a value of 40m.

Create an if else statement that returns giant! if the length exceeds 35, medium if the length is between 20 and 35, or small if teh length is \<= 20.

```{r}
blue_whale <- 40

if (blue_whale > 35){
  print("Giant!")
} else if (20 <= blue_whale & blue_whale<= 35) {
  print("Medium")
} else if (blue_whale < 20){
  print("small")
}
```

### Switch Statement

```{r}
housing_type <- "double"

switch(housing_type,
       "single" = print("400"),
       "double" = print("750"),
       "whole house" = print("1100")
)

if (housing_type == "whole house") {
  print("1100")
} else if (housing_type == "double"){
  print("750")
} else if (housing_type == "single") {
  print("400")
}
```

## For Loops

```{r}
height <- c(58,61,65,71,89,94,101)

height_ft  <- vector("numeric", length(height))

for (i in seq_along(height)){
  height_conv = height[i]/12 
  height_ft[i] = height_conv
}
print(height_ft)
```

```{r}
# mass <- c(58,61,65,71,89,94,101)
# 
# for (i in seq_along(mass)) {
#   mass_sum = mass[i] + mass[i+1]
#   print(mass_sum)

mass <- c(58,61,65,71,89,94,101)

for (i in seq(1, length(mass)-1)) {
  mass_sum = mass[i] + mass[i+1]
  print(mass_sum)
}
```

Write a for loop that calculates the value of hieght for each element divided by the mean of the entire height vector

```{r}
height_1 <- c(45,56,67,78,90,101,35,67,57,48)

for (i in seq_along(height_1)){
  std_val = height_1[i]/mean(height_1)
  print(std_val)
}
```

## For Loops with Conditional Statements

```{r}
library(palmerpenguins)

```

Write a for loop with an if statement that returns the means of all numeric vales in the dataset

```{r}
for (i in seq_along(penguins)){
  if (is.numeric (penguins[[i]])){
  mean_peng <- mean(penguins[[i]], na.rm = TRUE)
  print(mean_peng)}
}


```
